Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-11-15 manuscript/manuscript.Rmd
Adding word and figure counts

  - Main text (excludes the abstract, section titles, figure and table captions, funding statement, acknowledgments, and references): [X,XXX]
  - Number of figures: [X]
  - Number of tables: [X]

>>>>

  - Main text (excludes the abstract, section titles, figure and table captions, funding statement, acknowledgments, and references): 8,200
  - Number of figures: 6
  - Number of tables: 0
